Effectful Semantics for Substructural SSA

### 2023-11-17 pldi24/paper.tex
Yes!

  from \(\mb{T}\). Some important examples of submonads include:
    \item The \textbf{unit submonad} \(\eta\) of every monad \(\mb{T}\) with
    \(\eta(A) = \{\eta_A\;a \mid a \in A\}\).
    %; similarly, \(\mb{T}\) is itself a submonad of \(\mb{T}\). 
    \item Given submonads \(\mb{S}_i\) of \(\mb{T}\), their elementwise
    intersections \(\bigwedge_i\mb{S}_i = \lambda A. \bigcap_i \mb{S}_i\;A\) are
    submonads, forming a complete meet-semilattice with bottom \(\eta\) and top
    \(\mb{T}\),
    % ; this induces a complete lattice in the standard manner.
    \item In particular, the intersection of a relevant/affine/commutative
    submonad and another submonad is relevant/affine/commutative respectively.

@@

    \item Given a monoid \(M\) acting on sets \(I_i\) with action \(\cdot_i\) and
    stream actions \(\Theta_i: M^\omega \to I_i\), \(\Theta =
    \langle\Theta_i\rangle_i: M^\omega \to \Pi_iI_i\) is a stream action
    compatible with the action \(m \cdot l = (m \cdot_i l_i)_i\).

@@

  \mc{P}^+(A \times C + \mb{0}), \mc{P}^+(A \times C \times I) \subseteq
  \ms{Traces}\;\Theta\;A\) are submonads

@@

notion of refinement types, while at the same time giving us a nontrivial notion
of nonlinear types. Taking as objects pairs \((A, \Phi)\), where \(\Phi: A \to

>>>>

  from \(\mb{T}\). The \textbf{unit submonad} \(\eta\) of every monad \(\mb{T}\)
  is given by the map \(\eta(A) = \{\eta_A\;a \mid a \in A\}\). Given submonads
  \(\mb{S}_i\) of \(\mb{T}\), their elementwise intersections
  \(\bigwedge_i\mb{S}_i = \lambda A. \bigcap_i \mb{S}_i\;A\) are submonads,
  forming a complete meet-semilattice with bottom \(\eta\) and top \(\mb{T}\).
  In particular, the intersection of a relevant/affine/commutative submonad and
  another submonad is relevant/affine/commutative respectively.

@@

    % \item Given a monoid \(M\) acting on sets \(I_i\) with action \(\cdot_i\) and
    % stream actions \(\Theta_i: M^\omega \to I_i\), \(\Theta =
    % \langle\Theta_i\rangle_i: M^\omega \to \Pi_iI_i\) is a stream action
    % compatible with the action \(m \cdot l = (m \cdot_i l_i)_i\).

@@

  \mc{P}^+(A \times C + \mb{0}) \subseteq \ms{Traces}\;\Theta\;A\) is a submonad.

@@

notion of refinement types. Taking as objects pairs \((A, \Phi)\), where \(\Phi: A \to
